Comparing summed probability distributions of shoreline and radiocarbon dates from the Mesolithic Skagerrak coast of Norway

### 2023-06-14 analysis/paper/paper.Rmd
ADMUR for radiocarbon

All analyses done in this study were performed using the R programming language [@rcoreteam]. Underlying data and programming code used for the paper is available in a version-controlled online repository at X. This is structured as a research compendium following @marwick2018b, to allow for reproducibility of the results [see also @Marwick2017]. Analysis of the ^14^C-dates were done using the R package *rcarbon* [@crema2021]. The R package *shoredate* was used for performing and handling the shoreline dating of sites [@roalkvam2023b]. Finally, the package *ADMUR* [@timpson2021] was used for model comparison.

>>>>

All analyses done in this study were performed using the R programming language [@rcoreteam]. Underlying data and programming code used for the paper is available in a version-controlled online repository at X. This is structured as a research compendium following @marwick2018b, to allow for reproducibility of the results [see also @Marwick2017]. Analysis of the ^14^C-dates were done using the R package *ADMUR* [@timpson2021]. The R package *shoredate* was used for performing and handling the shoreline dating of sites [@roalkvam2023b], with repurposed code from both *ADMUR* and *rcarbon* [@crema2021] for Monte Carlo simulation and model comparison.
